\emph{icepack}: a novel glacier flow modeling package

### 2020-11-24 icepack.tex
Cut some redundant text

One key limitation of our approach is that users can change individual terms of the action functional but they cannot add or remove terms.
This calls for creating an entirely new diagnostic model.

One of our main design goals for icepack is to enable users to ``plug and play'' their own physics.
Since many aspects of glacier flow are not understood completely, we view extensibility as an essential requirement for any software package in this domain.
Writing the entire package in Python was necessary to meet this goal.
Many scientific software packages consist of a highly-optimized core library in C, C++, or Fortran, together with a wrapper that exposes this library to an interpreted language like Python.
This approach in principle offers the best of both worlds -- the runtime efficiency of a compiled language with the convenience and interactivity of an interpreted one.
Many practitioners, however, will use such a library entirely through the interpreted surface layer and have no familiarity with the language in which the fast core was written.
These users then have a steep learning curve to overcome when they need to modify functionality that lives in the core library, as they now need to learn an entirely new programming language.
Some low-level kernel code is always necessary for runtime efficiency but with Firedrake this responsibility is deferred to a code generator \citep{rathgeber2016firedrake}.
The average user can remain largely unaware of how the code generator works even when solving very advanced problems.

>>>>

One key limitation of our approach is that, while users can change what goes into one or more terms of the action functional, they cannot add or remove terms.
This case would call for writing a new diagnostic model.
